---
title: Fleet assignment
author: OZBAY Yasin - LHOEST Simon
date: Group 07
output:
  html_document:
    theme: paper
    highlight: monochrome
    toc: true
    toc_float: true
---
<style type="text/css">

body{ /* Normal  */
      font-size: 14px;
  }
</style>
  
```{r setup, include=FALSE}
source("mp_solver.R")
schedule <- fread("schedule.csv")
flight_info <- fread("flight_info.csv")
fleet_info <- fread("fleet_info.csv")

knitr::opts_chunk$set(echo = F, warning = F)
```

```{r code, include=FALSE}
lp_code <- "
set F;
set K;
set C;
set M;

param prev{k in M};
param c{i in F, j in K};
param N{j in K};
param s{i in F, k in M}, default 0;

var x{i in F, j in K}, binary;
var G{k in M, j in K} >= 0, integer;

s.t. Summ{i in F}: sum{j in K}x[i,j], == 1;
s.t. Ground{k in M, j in K}: G[prev[k],j] + sum{i in F}(s[i,k]*x[i,j]), == G[k,j];
s.t. Number{j in K}: sum{k in C}G[k,j], <= N[j];

minimize obj: sum{j in K, i in F}c[i,j]*x[i,j];
"

fleet_info[, Fleet := tstrsplit(Fleet, " ")[2]]

Nflight = nrow(flight_info)
Nfleet = nrow(fleet_info)
Nplane = fleet_info[,sum(Size)]

sch = merge(schedule, flight_info, by=c("Flight no.", "Origin", "Destination"),
              sort = FALSE, all = TRUE)

set_F = data.table(schedule[,`Flight no.`])

set_K = data.table(fleet_info$Fleet)

set_M = data.table(id = c(1:(Nflight*2))) 

temp1 = fleet_info[rep(1:.N, each=Nflight)]
temp2 = flight_info[rep(1:.N, Nfleet)]
final = cbind(temp2,temp1)
final[,OC := CASK*Seats*`Distance (km)`]
thefunc <- function(x, c, mean_val, sd_val)  {(x-c)*dnorm(x, mean = mean_val, sd = sd_val)}
final[, ES := integrate(function(x) (x-Seats)*dnorm(x, mean = `Demand (mean)`, sd = `Demand (sd)`), lower = Seats, upper = Inf)$value, .(`Flight no.`, Fleet)]
final[,SC := ES*RASK*`Distance (km)`*0.85]
param_c =data.table(final[,`Flight no.`],final[,Fleet],cost=final[, OC+SC])

param_N = data.table(fleet_info[,Fleet],fleet_info[,Size])

sch1 = copy(sch)
sch2 = copy(sch)
sch1 = sch1[,airprt:=sch[,Destination] ]
sch2 = sch2[,airprt:=sch[,Origin] ]
sch1 = sch1[,time:=sch$Arrival ]
sch2 = sch2[,time:=sch$Departure]
sch1 = sch1[,S:= 1 ]
sch2 = sch2[,S:= -1]

sch3 <- rbind(sch1,sch2)

sch3 <- sch3[order(sch3$airprt,sch3$time),]
param_s = data.table(sch3$`Flight no.`, sch3$airprt, sch3$S,c(1:(Nflight*2)))
setnames(param_s, c("V1","V2","V3","V4"),c("Flight", "Node","S", "id_node"))
param_s[,prev := shift(id_node,1),by=Node]
order=is.na(param_s$prev)
param_s[is.na(param_s$prev), prev:=param_s[, id_node[.N], Node]$V1]

param_prev = param_s[, .(id_node, prev)]
order=param_s[order,prev]
temp=data.table(Node=param_s[order,id_node],Overnight=param_s[order,S])
set_C = data.table(Node=temp[Overnight==1,Node])


param_s[,Node:=id_node] #Cleaning
param_s[,id_node:=NULL] 
param_s[,prev:=NULL]

vars <- list(set.F  = set_F,
            set.K   = set_K,
            set.C   = set_C,
            set.M   = set_M,
            par.prev= param_prev,
            par.c   = param_c,
            par.N   = param_N,
            par.s   = param_s,
            lp.code = lp_code)

example <- lp_solver(vars, T)
x=example$vars[var=="x"]
G=example$vars[var=="G"]

beurk = G[i1 %in% set_C$Node,]
setnames(beurk,c("i1","i2"),c("Node","Fleet"))
beurk[,Node:=as.integer(Node)]
beurk=merge(beurk,param_s,by="Node")
setnames(beurk,"Flight","Flight no.")
beurk=merge(beurk,schedule,by="Flight no.")
beurk=beurk[,.(Fleet,value,Destination)]

beurk[,value:=as.character(value)]
beurk[value=="1",value:="1 aircraft"]
beurk[value>"1 aircraft", value:=paste(value, 'aircrafts')]

beurk = dcast(beurk, Destination~Fleet,value.var="value")
beurk[is.na(beurk)]="-"

sol1 = beurk
sol2 = schedule[x$i2==fleet_info[1,Fleet]]
sol2$"Flight time" <- round(as.numeric(as.ITime(sol2$"Flight time")/3600), digits=1)
sol22= schedule[x$i2==fleet_info[2,Fleet]]
sol22$"Flight time" <- round(as.numeric(as.ITime(sol22$"Flight time")/3600), digits=1)

setnames(x,c("i1","i2"),c("Flight no.","Fleet"))
x[Fleet==fleet_info[1,Fleet],Fleet:=1]
x[Fleet==fleet_info[2,Fleet],Fleet:=2]
# fwrite(x[,.(`Flight no.`,Fleet)],file = "07_YVR_feel_dist.csv")
```
```{r code2, include=FALSE}
lp_code2 <- "
set F;
set K;
set C;
set M;

param prev{k in M};
param c{i in F, j in K};
param N{j in K};
param s{i in F, k in M}, default 0;

var x{i in F, j in K}, binary;
var G{k in M, j in K} >= 0, integer;

s.t. Summ{i in F}: sum{j in K}x[i,j], == 1;
s.t. Ground{k in M, j in K}: G[prev[k],j] + sum{i in F}s[i,k]*x[i,j], == G[k,j];
s.t. Number{j in K}: sum{k in C}G[k,j], <= N[j];

minimize obj: sum{k in C, j in K}G[k,j];
"
vars <- list(set.F  = set_F,
            set.K   = set_K,
            set.C   = set_C,
            set.M   = set_M,
            par.prev= param_prev,
            par.c   = param_c,
            par.N   = param_N,
            par.s   = param_s,
            lp.code = lp_code2)
example2 <- lp_solver(vars, T)
MOINS = Nplane-example2$optim
```
```{r code3, include=FALSE}
last <- data.table(AC1 = 0:sum(Nplane), AC2 = sum(Nplane):0)
last[,id:=1:nrow(last)]

notafor <- function(number) {
  param_N <- data.table(fleet_info[,Fleet],number)
  vars <- list(set.F  = set_F,
            set.K   = set_K,
            set.C   = set_C,
            set.M   = set_M,
            par.prev= param_prev,
            par.c   = param_c,
            par.N   = param_N,
            par.s   = param_s,
            lp.code = lp_code)
  example <- lp_solver(vars, T) 
  return(round(example$optim))
}

last[, cost := notafor(c(AC1,AC2)),by=id]
last[, id := NULL]
min = which(last[,3]==min(last[, 3]))[1]
```

<!-- Your report here -- NO LOOPS -->

# Solution

The minimum cost is **`r format(round(unlist(example$optim)), scientific=F)`€**. In this case, the fleet distribution is: 

```{r sol1, echo = F}
kable(sol1, caption = "Fleet distribution", align = rep("c", ncol(sol1)), col.names = c("Airport",paste(fleet_info[,Fleet]," fleet"))) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"),
                full_width = FALSE) 
```

The schedules for fleets `r unlist(fleet_info[1,Fleet])` and `r unlist(fleet_info[2,Fleet])` are: 

```{r sol2, echo = F}
kable(sol2, caption = paste(unlist(fleet_info[1,Fleet]),"schedule"), align = rep("c", ncol(sol2)), col.names = c("Flight no.", "Origin", "Departure time", "Destination", "Arrival time", "Flight time")) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"),
                full_width = FALSE)

kable(sol22, caption = paste(unlist(fleet_info[2,Fleet]),"schedule"), align = rep("c", ncol(sol22)), col.names = c("Flight no.", "Origin", "Departure time", "Destination", "Arrival time", "Flight time")) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"),
                full_width = FALSE)
``` 

# Scenario analysis

## Case 1

> Minimum number of aircrafts to cover all flights

The minimum number of aircrafts is **`r example2$optim`**, `r MOINS` less than our current fleet.

## Case 2

> Minimum number of aircrafts to cover all flights

The best combination with our fleet size is formed by `r unlist(last[min,1])` `r unlist(fleet_info[1,Fleet])` and `r unlist(last[min,2])` `r unlist(fleet_info[2,Fleet])` with a minimum cost of `r format(round(unlist(last[min,3])),scientific=F)`€. All possible combinations for our fleet size are:

```{r last, echo = F}
kable(last, align = rep("c", ncol(last)), col.names = c(paste(fleet_info[,Fleet]," aircrafts"), "Total daily cost (€)")) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"),
                full_width = FALSE) %>%
  row_spec(min, bold = T, background = "#FFFDE9")
``` 



<div class = "tocify-extend-page" data-unique = "tocify-extend-page" style = "height: 0;"></div>